Computational methods in landscape ecology

### 2024-06-01 Sections/software.qmd
adds software ideas

@@

### R
<!-- Hesselbarth -->

@@

>>>>

<!-- "The future applications of landscape pattern metrics will almost certainly depend on the software and analysis tools available" -- @costanzaDescribingAnalyzingLandscape2019 -->

@@

### R
<!-- Hesselbarth -->
landscapemetrics
geodiv
vectormetrics
bespatial
motif
?GLCMTextures
?rasterdiv
?terra

@@

## Other open source software

GuidosToolbox
?GRASS GIS
?QGIS: LecoS plugin
